### 2014-07-31 paper/paper.tex
Added a section about the number of features

%TODO write about the number of features

>>>>

Number of features retained varies from Tweet to Tweet. To summarize the number
of features retained after different process Table \ref{table:numfeatures}
presents the mean number of features per Tweet for positive, neutral, negative
examples as well as an overall average.

\begin{table}[H]
    \begin{center}
    \begin{tabular}{|c||r|r|r|r|}
        \hline
                               & Positive & Neutral & Negative & Overall \\
        \hline
        \textit{a}, \textit{i} & 14.85    & 14.06   & 15.10    & 14.49 \\
        \textit{b}, \textit{j} & 14.91    & 14.30   & 15.30    & 14.67 \\
        \textit{c}, \textit{k} & 15.95    & 15.40   & 16.33    & 15.73 \\
        \textit{d}, \textit{l} & 17.13    & 16.86   & 17.41    & 17.04 \\
        \textit{e}, \textit{m} & 18.54    & 17.81   & 18.82    & 18.22 \\
        \textit{f}, \textit{n} & 18.43    & 17.87   & 18.85    & 18.21 \\
        \textit{g}, \textit{o} & 19.64    & 19.15   & 20.05    & 19.46 \\
        \textit{h}, \textit{p} & 20.65    & 20.45   & 20.96    & 20.58 \\
        \hline
    \end{tabular}
    \end{center}
    \caption{The average number of features in each experiment}
    \label{table:numfeatures}
\end{table}

As presented in Table \ref{table:numfeatures}, the number of features decreases
each time a feature set simplification method is turned on. Normalization does
not appear to significantly reduce the number of features per Tweet. This make
sense because the number of features in would only be reduced if it contained
tokens that were different before simplification and were the same after (e.g.
A Tweet that contained `2' and `3' before normalization would only contain the
feature `\#NUM' after normalization).
